---
title: "samql manuscript results code"
output:
  pdf_document: default
  html_notebook: default
---

# Table of Contents

* [Generating samples](#generating-samples)
* [Running query tests](#running-query-tests)
* [Aggregating data](#aggregating-data)
* [Creating Figs](#figs)

# Generating samples


Generating 10 different sizes

save in a .sh script, chmod 755 if needed
```{bash eval=F}
FILE='/data/chris/wgEncodeCaltechRnaSeqGm12878R1x75dSplicesRep1V2.bam'
cd ~

for i in {i..9}
do
samtools view -bs 0.$i $FILE > /data/chris/testSam$i.bam
done
samtools view -b $FILE > /data/chris/testSam10.bam

```


# Running query tests

Empty Query. Unused in manuscript, was used to test printing time
```{bash}
echo Empty
cd ~
for j in {1..10}
do
FILE=$(printf '/data/chris/testSam%s.bam' "$j")
RESULTSFQ1=$(printf '/data/chris/samResults/testSamResultsEmpty2Samql1c%s.txt' "$j")
RESULTSFQ2=$(printf '/data/chris/samResults/testSamResultsEmpty2Samql2c%s.txt' "$j")
RESULTSFT=$(printf '/data/chris/samResults/testSamResultsEmpty2Samtools%s.txt' "$j")
RESULTSFB=$(printf '/data/chris/samResults/testSamResultsEmpty2Bash%s.txt' "$j")
samtools index $FILE
for i in {1..10}
do
/usr/bin/time --format="%e" --output=$RESULTSFQ1 -a samql --parr 1 $FILE  > /dev/null
/usr/bin/time --format="%e" --output=$RESULTSFQ2 -a samql --parr 2 $FILE  > /dev/null
/usr/bin/time --format="%e" --output=$RESULTSFT -a samtools view $FILE > /dev/null
/usr/bin/time --format="%e" --output=$RESULTSFB -a samtools view $FILE > /dev/null
/usr/bin/time --format="%e" --output=$RESULTSFQ1 -a samql -c --parr 1 $FILE  > /dev/null
/usr/bin/time --format="%e" --output=$RESULTSFQ2 -a samql -c --parr 2 $FILE  > /dev/null
/usr/bin/time --format="%e" --output=$RESULTSFT -a samtools view -c $FILE > /dev/null
/usr/bin/time --format="%e" --output=$RESULTSFB -a samtools view $FILE | wc -l > /dev/null
done
done


/usr/bin/time samql --parr 2 $FILE > /dev/null
/usr/bin/time samtools view $FILE > /dev/null

```



Complex Query

```{bash eval=F}
echo Complex Query
cd ~
for j in {1..10}
do
FILE=$(printf '/data/chris/testSam%s.bam' "$j")
RESULTSFQ1=$(printf '/data/chris/samResults/testSamResultsComplex2Samql1c%s.txt' "$j")
RESULTSFQ2=$(printf '/data/chris/samResults/testSamResultsComplex2Samql2c%s.txt' "$j")
RESULTSFT=$(printf '/data/chris/samResults/testSamResultsComplex2Samtools%s.txt' "$j")
RESULTSFB=$(printf '/data/chris/samResults/testSamResultsComplex2Bash%s.txt' "$j")
samtools index $FILE
for i in {1..10}
do
/usr/bin/time --format="%e" --output=$RESULTSFQ1 -a samql --where "RNAME = 'chr1' AND POS > 14800 AND POS < 15000" --parr 1 $FILE  > /dev/null
/usr/bin/time --format="%e" --output=$RESULTSFQ2 -a samql --where "RNAME = 'chr1' AND POS > 14800 AND POS < 15000" --parr 2 $FILE  > /dev/null
/usr/bin/time --format="%e" --output=$RESULTSFT -a samtools view $FILE 'chr1:14800-15000' > /dev/null
/usr/bin/time --format="%e" --output=$RESULTSFB -a samtools view $FILE | awk '$3 == "chr1" && $4 > 14800 && $4 < 15000' > /dev/null
/usr/bin/time --format="%e" --output=$RESULTSFQ1 -a samql -c --where "RNAME = 'chr1' AND POS > 14800 AND POS < 15000" --parr 1 $FILE  > /dev/null
/usr/bin/time --format="%e" --output=$RESULTSFQ2 -a samql -c --where "RNAME = 'chr1' AND POS > 14800 AND POS < 15000" --parr 2 $FILE  > /dev/null
/usr/bin/time --format="%e" --output=$RESULTSFT -a samtools view -c $FILE 'chr1:14800-15000' > /dev/null
/usr/bin/time --format="%e" --output=$RESULTSFB -a samtools view $FILE | awk '$3 == "chr1" && $4 > 14800 && $4 < 15000' | wc -l > /dev/null
done
done
```



Tag query
```{bash eval=F}
echo TagCC
cd ~
for j in {1..10}
do
FILE=$(printf '/data/chris/testSam%s.bam' "$j")
RESULTSFQ1=$(printf '/data/chris/samResults/testSamResultsTagCCSamql1c%s.txt' "$j")
RESULTSFQ2=$(printf '/data/chris/samResults/testSamResultsTagCCSamql2c%s.txt' "$j")
RESULTSFT=$(printf '/data/chris/samResults/testSamResultsTagCCSamtools%s.txt' "$j")
RESULTSFB=$(printf '/data/chris/samResults/testSamResultsTagCCBash%s.txt' "$j")
samtools index $FILE
for i in {1..10}
do
/usr/bin/time --format="%e" --output=$RESULTSFQ1 -a samql --where "CC:Z = chr15" --parr 1 $FILE  > /dev/null
/usr/bin/time --format="%e" --output=$RESULTSFQ2 -a samql --where "CC:Z = chr15" --parr 2 $FILE  > /dev/null
/usr/bin/time --format="%e" --output=$RESULTSFT -a samtools view -d CC:chr15 $FILE  > /dev/null
/usr/bin/time --format="%e" --output=$RESULTSFB -a samtools view $FILE | grep -P '^@|CC:Z:chr15\b' > /dev/null
/usr/bin/time --format="%e" --output=$RESULTSFQ1 -a samql -c --where "CC:Z = chr15" --parr 1 $FILE  > /dev/null
/usr/bin/time --format="%e" --output=$RESULTSFQ2 -a samql -c --where "CC:Z = chr15" --parr 2 $FILE  > /dev/null
/usr/bin/time --format="%e" --output=$RESULTSFT -a samtools view -c -d CC:chr15 $FILE  > /dev/null
/usr/bin/time --format="%e" --output=$RESULTSFB -a samtools view $FILE | grep -P '^@|CC:Z:chr15\b' | wc -l > /dev/null
done
done
```

```{bash eval=F}
echo TagNH
cd ~
for j in {1..10}
do
FILE=$(printf '/data/chris/testSam%s.bam' "$j")
RESULTSFQ1=$(printf '/data/chris/samResults/testSamResultsTagNHSamql1c%s.txt' "$j")
RESULTSFQ2=$(printf '/data/chris/samResults/testSamResultsTagNHSamql2c%s.txt' "$j")
RESULTSFT=$(printf '/data/chris/samResults/testSamResultsTagNHSamtools%s.txt' "$j")
RESULTSFB=$(printf '/data/chris/samResults/testSamResultsTagNHBash%s.txt' "$j")
samtools index $FILE
for i in {1..10}
do
/usr/bin/time --format="%e" --output=$RESULTSFQ1 -a samql --where "NH:i >= 2" --parr 1 $FILE  > /dev/null
/usr/bin/time --format="%e" --output=$RESULTSFQ2 -a samql --where "NH:i >= 2" --parr 2 $FILE  > /dev/null
/usr/bin/time --format="%e" --output=$RESULTSFT -a echo  > /dev/null
/usr/bin/time --format="%e" --output=$RESULTSFB -a samtools view $FILE | perl -n -e'/NH:i:(\d+)/; if($1 >= 2) {print}' > /dev/null
/usr/bin/time --format="%e" --output=$RESULTSFQ1 -a samql -c --where "NH:i >= 2" --parr 1 $FILE  > /dev/null
/usr/bin/time --format="%e" --output=$RESULTSFQ2 -a samql -c --where "NH:i >= 2" --parr 2 $FILE  > /dev/null
/usr/bin/time --format="%e" --output=$RESULTSFT -a echo  > /dev/null
/usr/bin/time --format="%e" --output=$RESULTSFB -a samtools view $FILE | perl -n -e'/NH:i:(\d+)/; if($1 >= 2) {print}'| wc -l > /dev/null
done
done
```

Parallelization tests, same tests as above
```{bash eval=F}
FILE='/data/chris/testSam10.bam'

echo Parr Complex
cd ~
for p in 1 2 4 8
do
RESULTSFQ=$(printf '/data/chris/samResults/testSamResultsComplex2ParrSamql%s.txt' "$p")
for i in {1..10}
do
/usr/bin/time --format="%e" --output=$RESULTSFQ -a samql --where "RNAME = 'chr1' AND POS > 14800 AND POS < 15000" --parr $p $FILE  > /dev/null
done
done

echo Parr TagCC
cd ~
for p in 1 2 4 8
do
RESULTSFQ=$(printf '/data/chris/samResults/testSamResultsTagCCParrSamql%s.txt' "$p")
for i in {1..10}
do
/usr/bin/time --format="%e" --output=$RESULTSFQ -a samql --where "CC:Z = chr15" --parr $p $FILE  > /dev/null
done
done

echo Parr TagNH
cd ~
for p in 1 2 4 8
do
RESULTSFQ=$(printf '/data/chris/samResults/testSamResultsTagNHParrSamql%s.txt' "$p")
for i in {1..10}
do
/usr/bin/time --format="%e" --output=$RESULTSFQ -a samql --where "NH:i >= 2" --parr $p $FILE  > /dev/null
done
done

```


# Compiling data
Aggregate the data to transfer to laptop
```{R eval=F}
testnames = c("Empty2","Complex2", "TagCC", "TagNH")

samResultsAll = array(0, c(length(testnames), 4, 10, 20))  #Querytype, method, %size, trial

for (i in 1:length(testnames)) {
	for (k in 1:10) {
		samResultsAll[i, 1, k, ] = 
			read.table(sprintf("/data/chris/samResults/testSamResults%sSamql1c%s.txt", testnames[i], k))$V1[1:20]
		samResultsAll[i, 2, k, ] = 
			read.table(sprintf("/data/chris/samResults/testSamResults%sSamql2c%s.txt", testnames[i], k))$V1[1:20]
		samResultsAll[i, 3, k, ] = 
			read.table(sprintf("/data/chris/samResults/testSamResults%sSamtools%s.txt", testnames[i], k))$V1[1:20]
		samResultsAll[i, 4, k, ] = 
			read.table(sprintf("/data/chris/samResults/testSamResults%sBash%s.txt", testnames[i], k))$V1[1:20]
	}
}

saveRDS(samResultsAll, "/data/chris/samResults/testSamResults2All.rds")
```


Aggregating parr
```{R eval=F}
testnames = c("Complex2", "TagCC", "TagNH")

samResultsAll = array(0, c(length(testnames), 1, 4, 10))  #Querytype, method, %size, trial

for (i in 1:length(testnames)) {
	for (k in 1:4) {
		samResultsAll[i, 1, k, ] = 
			read.table(sprintf("/data/chris/samResults/testSamResults%sParrSamql%s.txt", testnames[i], 2^(k-1)))$V1[1:10]
	}
}

saveRDS(samResultsAll, "/data/chris/samResults/testSamResults2ParrAll.rds")
```


# Figs

```{r eval=F}
samResultsAll = readRDS("~/testSamResults2All.rds")
testnames = c("Empty2","Complex2", "TagCC", "TagNH")

for (i in 2:length(testnames)) {
	pdf(sprintf("~/testSamResults%s.pdf",testnames[i]), height = 4, width = 3)
	plot(0, type = 'n', xlim = c(1,100), ylim = c(0, max(samResultsAll[-1,,,])), main = NULL,
		 xlab = "% of total data", ylab = "Time (secs)")
	legend("topleft", legend = c("samql (1 thread)","samql (2)","samtools","bash (2)"), 
		   col = c(rgb(0,77,77,maxColorValue = 255),
		   		rgb(70,130,180, maxColorValue = 255),
		   		rgb(235,193,7, maxColorValue = 255),
		   		rgb(178,34,34, maxColorValue = 255)), 
		   pch = 16, cex = 0.8, bty="n")
	for (k in 1:10) {
		points(10*rep(k,10), samResultsAll[i,1,k,2*1:10-1], col = rgb(0,77,77,216, maxColorValue = 255))
		points(10*rep(k,10), samResultsAll[i,3,k,2*1:10-1], col = rgb(235,193,7,216, maxColorValue = 255))	
		points(10*rep(k,10)-1, samResultsAll[i,4,k,2*1:10-1], col = rgb(178,34,34,216, maxColorValue = 255))
		points(10*rep(k,10), samResultsAll[i,2,k,2*1:10-1], col = rgb(70,130,180,216, maxColorValue = 255))

		
	}
	dev.off()

}

for (i in 2:length(testnames)) {
	pdf(sprintf("~/testSamResults%sCount.pdf",testnames[i]), height = 4, width = 3)
	plot(0, type = 'n', xlim = c(1,100), ylim = c(0, max(samResultsAll[-1,,,])), main = NULL,
		 xlab = "% of total data", ylab = "Time (secs)")
	legend("topleft", legend = c("samql (1 thread)","samql (2)","samtools","bash (2)"), 
		   col = c(rgb(0,77,77,maxColorValue = 255),
		   		rgb(70,130,180, maxColorValue = 255),
		   		rgb(235,193,7, maxColorValue = 255),
		   		rgb(178,34,34, maxColorValue = 255)), 
		   pch = 16, cex = 0.8, bty="n")	
	for (k in 1:10) {
		points(10*rep(k,10), samResultsAll[i,1,k,2*1:10], col = rgb(0,77,77,216, maxColorValue = 255))
		points(10*rep(k,10), samResultsAll[i,3,k,2*1:10], col = rgb(235,193,7,216, maxColorValue = 255))	
		points(10*rep(k,10)-1, samResultsAll[i,4,k,2*1:10], col = rgb(178,34,34,216, maxColorValue = 255))
		points(10*rep(k,10), samResultsAll[i,2,k,2*1:10], col = rgb(70,130,180,216, maxColorValue = 255))

		
	}
	dev.off()

}
```


```{r eval=F}
samResultsParrAll = readRDS("~/testSamResults2ParrAll.rds")
testnames = c("Complex2", "TagCC", "TagNH")

for (i in 1:length(testnames)) {
	pdf(sprintf("~/testSamResults%sParr.pdf",testnames[i]), height = 4, width = 3)

	plot(0, type = 'n', xlim = c(0,3), ylim = c(0, max(samResultsParrAll)), main = testnames[i],
		 xlab = "log2 N Cores", ylab = "Time (secs)")
	#legend("topleft", legend = c("samql"), col = c("blue"), pch = "-")
	for (k in 1:4) {
		points(rep(k-1,10), samResultsParrAll[i,1,k,], col = "blue")
	}
	dev.off()
}
```

